Hydra Battles and Cie

### 2021-08-04 doc/part-hydras.tex
converting chapter 3 to alectryon (continued)

We can define on \texttt{Omega2} an addition which extends the addition on \texttt{nat}.

\begin{Coqsrc}
Definition  plus (alpha beta : t) : t :=
  match alpha,beta with
  | (0, b), (0, b') => (0, b + b')
  | (0,0), y  => y
  | x, (0,0)  => x
  | (0, b), (S n', b') => (S n', b')
  | (S n, b), (S n', b') => (S n + S n', b')
  | (S n, b), (0, b') => (S n, b + b')
   end.

Infix "+" := plus : o2_scope.
\end{Coqsrc}

Please note that this operation is not commutative:

\begin{Coqsrc}
Example non_commutativity_of_plus :  omega + 3 <> 3 + omega.
Proof.
  cbn.
\end{Coqsrc}

\begin{Coqanswer}
1 subgoal (ID 237)

  ============================
(1, 3) <> omega.
\end{Coqanswer}

\begin{Coqsrc}
 discriminate.
Qed.
\end{Coqsrc}

>>>>

We can define on \texttt{Omega2} an addition which extends the addition on \texttt{nat}. Please note that this operation is not commutative:

\input{movies/snippets/ON_Omega2/plusDef}
